Sound Automated Synthesis of Digital Controllers

### 2016-10-12 paper/paper.tex
editing sec 4.3

If the result of the {\sc Uncertainty} verification is that
$\neg \phi_{stability}$ is unsatisfiable for $S(z)$, then we pass 
the current candidate solution to the {\sc Precision} verification sub-phase, 
which checks the propagation of the error in the fixed-point 
calculations. If this check returns $false$, then we 
increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise} phase
with an empty {\sc inputs} set.

@@

In the second {\sc verify} phase, we check whether the current candidate
solution above is the final solution. It is not and the verifier signals
that it is due to lack of precision. We thus increase our precision to
$I_b=20,F_b=28$.
%
We stay in the {\sc verify} phase and receive a new counterexample at
higher precision:
%
$$
\begin{array}{ll}
\Delta N_G(z) {=} 0.026314\\
\Delta D_G(z) {=} 0.999024z{-}1.004785
\end{array}
$$
%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
Since previous counterexamples were attained at lower precision, we 
remove them from the counterexample set. In the next {\sc synthesise}
phase, we get a new candidate solution that holds for the newly
inserted counterexample:

>>>>

If the result of the {\sc Uncertainty} verification is that
the system is stable for the current candidate solution,
then we pass this solution to the {\sc Precision} verification sub-phase, 
which checks the propagation of the error in the fixed-point 
calculations. If this check returns $false$, then we 
increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise} phase
with an empty {\sc inputs} set.
Otherwise, we found a full solution for our synthesis problem
and we are done.

@@

In the second {\sc verify} phase, we check whether the current candidate
solution above is the final solution. It is not and the verifier signals
that it is due to lack of precision. We thus increase our precision to
$I_b=20,F_b=28$.
%
We stay in the {\sc verify} phase and receive a new counterexample at
higher precision:
\cdsay{Pascal, this sounds confusing. if you want to increase precision on-the-fly, 
then this illustration doesn't follow the general diagram in Fig.5. 
We need to decide which direction we keep.}
%
$$
\begin{array}{ll}
\Delta N_G(z) {=} 0.026314\\
\Delta D_G(z) {=} 0.999024z{-}1.004785
\end{array}
$$
%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
Since previous counterexamples were attained at lower precision, we 
remove them from the counterexample set. In the next {\sc synthesise}
phase, we get a new candidate solution that holds for the newly
inserted counterexample:
